R Notebook

### 2017-05-10 paper.Rnw

>>>>

The Zero Inflated Poisson (ZIP) model has two parameters. The parameter p is the probability of a structural zero, and $\lambda$ corresponds to the parameter in a typical Poisson model. For a single observation x, the probability density is:

\noindent Bayarri, Berger, and Datta (2008) suggest using the prior distribution $\pi(\lambda, p) \propto \frac{1}{\sqrt{\lambda}}I(0<p<1)$. This gives us the following posterior
